### 2024-09-26 manuscript.tex
Various additions

\begin{table}[p!]
% TODO: Add sampling intervals.
\caption{
An overview of the analysed voyages, campaigns and stations. Start, end, and days
(UTC; inclusive) indicate the time period when the vessel was south of 40°S.
Abbreviations: ceilometer (ceil.), Australia (AU), New Zealand (NZ), South
America (SA), Atlantic Ocean (AO) and Africa (AF). The number of days is
rounded to the nearest integer. CL51/31 indicates CL51 configured to emulate
CL31.
}
\label{tab:voyages}
\small
\begin{tabular}{llllllr}
\textbf{Name} & \textbf{Vessel or station} & \textbf{Ceil.} & \textbf{Region} & \textbf{Start} & \textbf{End} & \textbf{Days}\\
\hline
AA15-16  & RSV \emph{Aurora Australis}   & CL51    & AU       & 2015-10-22 & 2016-02-22 & 124 \\
HMNZSW16 & HMNZS \emph{Wellington}       & CHM 15k & NZ       & 2016-11-23 & 2016-12-19 & 27 \\
MARCUS   & RSV \emph{Aurora Australis}   & CL51    & AU       & 2017-10-29 & 2018-03-26 & 149 \\
MICRE    & Macquarie Is. station         & CL51    & AU/NZ    & 2016-04-03 & 2018-03-14 & 710 \\
NBP1704  & RV \emph{Nathaniel B. Palmer} & CHM 15k & NZ       & 2017-04-14 & 2017-06-08 & 55 \\
PS77/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2010-12-01 & 2011-02-04 & 65 \\
PS77/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-02-07 & 2011-04-14 & 66 \\
PS79/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-12-06 & 2012-01-02 & 27 \\
PS79/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-01-10 & 2012-03-10 & 61 \\
PS79/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-03-14 & 2012-04-08 & 26 \\
PS81/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-12-02 & 2013-01-18 & 47 \\
PS81/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-01-22 & 2013-03-17 & 55 \\
PS81/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-03-18 & 2013-04-16 & 30 \\
PS81/5   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-04-20 & 2013-05-23 & 33 \\
PS81/6   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-06-10 & 2013-08-12 & 63 \\
PS81/7   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-08-15 & 2013-10-14 & 60 \\
PS81/8   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-11-12 & 2013-12-14 & 31 \\
PS81/9   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-12-21 & 2014-03-02 & 71 \\
PS89     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2014-12-05 & 2015-01-30 & 56 \\
PS96     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2015-12-08 & 2016-02-14 & 68 \\
PS97     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-02-15 & 2016-04-06 & 52 \\
PS103    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-12-18 & 2017-02-02 & 46 \\
PS104    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2017-02-08 & 2017-03-18 & 39 \\
PS111    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-01-21 & 2018-03-14 & 52 \\
PS112    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-03-18 & 2018-05-05 & 49 \\
PS117    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-12-18 & 2019-02-07 & 51 \\
PS118    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2019-02-18 & 2019-04-08 & 50 \\
PS123    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-01-10 & 2021-01-31 & 21 \\
PS124    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-02-03 & 2021-03-30 & 55 \\
TAN1502  & RV \emph{Tangaroa}            & CL51/31 & NZ       & 2015-01-20 & 2015-03-12 & 51 \\
TAN1702  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2017-03-09 & 2017-03-31 & 23 \\
TAN1802  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2018-02-07 & 2018-03-20 & 41 \\
\hline
\textbf{Total} &                         &         &          &            &            & \textbf{2421}\\
\end{tabular}
\normalsize
\end{table}

@@

\subsection{Vaisala CL51}
\label{sec:cl51}

The Vaisala CL51 (photo in Fig. \ref{fig:map}d) is a ceilometer operating at a
near-infrared wavelength of 910 nm. CL51 can also be configured to emulate the
Vaisala CL31. The maximum range is 15.4 km (CL51), 7.7 km (CL31 emulation mode
with 5 m vertical resolution), and 7.550 km (CL31 emulation mode with 10 m
vertical resolution). The vertical resolution is 10 m (5 m configurable), and
the sampling (temporal) resolution is 6 s (AA15‐16, MARCUS, and MICRE), 36 s
(RV \emph{Polarstern}), and about 2.37 s (TAN1502). From the MARCUS and MICRE
campaigns, unlike raw instrument data available for the other voyages and
stations, the Vaisala CL51 data were made available by the Atmospheric
Radiation Measurement (ARM) processed to a maximum range of 7.545 km, a
vertical resolution of 30 m, and sampling resolution of 16 s. The wavelength of
910 nm is affected by water vapour absorption of about 20\% in the
mid-latitudes \citep{wiegner2015,wiegner2019}.  The instrument data files
containing raw uncalibrated backscatter were first converted to NetCDF with
cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the
ALCF (Section \ref{sec:alcf}) to produce absolutely calibrated attenuated
volume backscattering coefficinet (AVBC), cloud mask, cloud occurrence by
height and the total cloud fraction.  The Vaisala CL51 instruments were used on
most of the voyages and stations analysed here. Fig. \ref{fig:example}a shows
an example of derived from the CL51 instrument.

@@

We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener
Institute and Pangaea, the AA15-16 dataset provided by the Australian Antarctic
Division (AAD) and University of Canterbury (UC), RV \emph{Tangaroa} datasets
provided by the National Institute of Water and Atmospheric Research and UC,
the NBP1704 dataset provided by the National Science Foundation, Cooperative
Institute for Research in Environmental Sciences, University of Colorado and
UC, the HMNZSW16 dataset provided by the Royal New Zealand Navy and UC, the
MARCUS dataset provided by the Atmospheric Radiation Measurement (ARM), AAD and
UC, and the MICRE dataset provided by ARM, the Australian Bureau of
Meteorology, AAD and UC. We thank the scientific staff, the crew, and everyone
involved in collecting data on the voyages and stations, especially Kelly
Schick, Peter Guest, John J.  Cassano, Simon Parsons, Graeme Plank, Sally
Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey (†), Simon P.  Alexander
and Alex Schuddeboom. We acknowledge the ICON model output provided by the
nextGEMS project and the Deutsches Klimarechenzentrum (DKRZ), reanalysis
dataset ERA5 provided by the Copernicus Climate Change Service and MERRA-2
provided by the Global Modeling and Assimilation Office. We dedicate this study
to the memory of Mike J. Harvey, who very substantially contributed to
obtaining atmospheric measurments on the RV \emph{Tangaroa} voyages used in
this study.

>>>>

\begin{table}[p!]
% TODO: Add sampling intervals.
\caption{
An overview of the analysed voyages, campaigns and stations. Start, end, and days
(UTC; inclusive) indicate the time period when the vessel was south of 40°S.
Abbreviations: ceilometer (ceil.), Australia (AU), New Zealand (NZ), South
America (SA), Atlantic Ocean (AO) and Africa (AF). The number of days is
rounded to the nearest integer. CL51/31 indicates CL51 configured to emulate
CL31.
}
\label{tab:voyages}
\small
\begin{tabular}{llllllr}
\textbf{Name} & \textbf{Vessel or station} & \textbf{Ceil.} & \textbf{Region} & \textbf{Start} & \textbf{End} & \textbf{Days}\\
\hline
AA15-16  & RSV \emph{Aurora Australis}   & CL51    & AU       & 2015-10-22 & 2016-02-22 & 124 \\
HMNZSW16 & HMNZS \emph{Wellington}       & CHM 15k & NZ       & 2016-11-23 & 2016-12-19 & 27 \\
MARCUS   & RSV \emph{Aurora Australis}   & CT25K   & AU       & 2017-10-29 & 2018-03-26 & 149 \\
MICRE    & Macquarie Is. station         & CT25K   & AU/NZ    & 2016-04-03 & 2018-03-14 & 710 \\
NBP1704  & RV \emph{Nathaniel B. Palmer} & CHM 15k & NZ       & 2017-04-14 & 2017-06-08 & 55 \\
PS77/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2010-12-01 & 2011-02-04 & 65 \\
PS77/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-02-07 & 2011-04-14 & 66 \\
PS79/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-12-06 & 2012-01-02 & 27 \\
PS79/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-01-10 & 2012-03-10 & 61 \\
PS79/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-03-14 & 2012-04-08 & 26 \\
PS81/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-12-02 & 2013-01-18 & 47 \\
PS81/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-01-22 & 2013-03-17 & 55 \\
PS81/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-03-18 & 2013-04-16 & 30 \\
PS81/5   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-04-20 & 2013-05-23 & 33 \\
PS81/6   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-06-10 & 2013-08-12 & 63 \\
PS81/7   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-08-15 & 2013-10-14 & 60 \\
PS81/8   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-11-12 & 2013-12-14 & 31 \\
PS81/9   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-12-21 & 2014-03-02 & 71 \\
PS89     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2014-12-05 & 2015-01-30 & 56 \\
PS96     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2015-12-08 & 2016-02-14 & 68 \\
PS97     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-02-15 & 2016-04-06 & 52 \\
PS103    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-12-18 & 2017-02-02 & 46 \\
PS104    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2017-02-08 & 2017-03-18 & 39 \\
PS111    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-01-21 & 2018-03-14 & 52 \\
PS112    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-03-18 & 2018-05-05 & 49 \\
PS117    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-12-18 & 2019-02-07 & 51 \\
PS118    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2019-02-18 & 2019-04-08 & 50 \\
PS123    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-01-10 & 2021-01-31 & 21 \\
PS124    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-02-03 & 2021-03-30 & 55 \\
TAN1502  & RV \emph{Tangaroa}            & CL51/31 & NZ       & 2015-01-20 & 2015-03-12 & 51 \\
TAN1702  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2017-03-09 & 2017-03-31 & 23 \\
TAN1802  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2018-02-07 & 2018-03-20 & 41 \\
\hline
\textbf{Total} &                         &         &          &            &            & \textbf{2421}\\
\end{tabular}
\normalsize
\end{table}

@@

\subsection{Vaisala CL51 and CT25K}
\label{sec:cl51}

The Vaisala CL51 (photo in Fig. \ref{fig:map}d) is a ceilometer operating at a
near-infrared wavelength of 910 nm. CL51 can also be configured to emulate the
Vaisala CL31. The maximum range is 15.4 km (CL51), 7.7 km (CL31 emulation mode
with 5 m vertical resolution), and 7.550 km (CL31 emulation mode with 10 m
vertical resolution). The vertical resolution is 10 m (5 m configurable), and
the sampling (temporal) resolution is 6 s (AA15‐16, MARCUS, and MICRE), 36 s
(RV \emph{Polarstern}), and about 2.37 s (TAN1502). From the MARCUS and MICRE
campaigns, unlike raw instrument data available for the other voyages and
stations, the Vaisala CT25K data were made available by the Atmospheric
Radiation Measurement (ARM) processed to a maximum range of 7.545 km, a
vertical resolution of 30 m, and sampling resolution of 16 s. The wavelength of
910 nm is affected by water vapour absorption of about 20\% in the
mid-latitudes \citep{wiegner2015,wiegner2019}.  The instrument data files
containing raw uncalibrated backscatter were first converted to NetCDF with
cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the
ALCF (Section \ref{sec:alcf}) to produce absolutely calibrated attenuated
volume backscattering coefficinet (AVBC), cloud mask, cloud occurrence by
height and the total cloud fraction.  The Vaisala CL51 instruments were used on
most of the voyages and stations analysed here. Fig. \ref{fig:example}a shows
an example of derived from the CL51 instrument.

@@

We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener
Institute and Pangaea, the AA15-16 dataset provided by the Australian Antarctic
Division (AAD) and University of Canterbury (UC), RV \emph{Tangaroa} datasets
provided by the National Institute of Water and Atmospheric Research and UC,
the NBP1704 dataset provided by the National Science Foundation, Cooperative
Institute for Research in Environmental Sciences, University of Colorado and
UC, the HMNZSW16 dataset provided by the Royal New Zealand Navy and UC, the
MARCUS dataset provided by the Atmospheric Radiation Measurement (ARM) and AAD,
and the MICRE dataset provided by ARM, the Australian Bureau of Meteorology,
and AAD. We thank the scientific staff, the crew, and everyone involved in
collecting data on the voyages and stations, especially Kelly Schick, Peter
Guest, John J.  Cassano, Simon Parsons, Graeme Plank, Sally Garrett, Jamie
Halla, Sean Hartery, Mike J.  Harvey (†), Simon P.  Alexander and Alex
Schuddeboom. We acknowledge the ICON model output provided by the nextGEMS
project and the Deutsches Klimarechenzentrum (DKRZ), reanalysis dataset ERA5
provided by the Copernicus Climate Change Service and MERRA-2 provided by the
Global Modeling and Assimilation Office. We dedicate this study to the memory
of Mike J. Harvey, who very substantially contributed to obtaining the
atmospheric measurments on the RV \emph{Tangaroa} voyages used in this study.
